Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-07-17 ch04-lrmhinf/lrmhinf.tex
Define T(P,C), adjust some figures

\subsection{Measurement \& Control Framework}
\label{sec:lrmhinf:control}
The experiments on the \gls{AVIS} are carried out in closed-loop (\figref{fig:lrmhinf:tpc}) with $r_2 = 0$.
%TODO: define T(P,C) formally
The controller $\Controller=\experimental\Controller$ is a diagonal \gls{PI} regulator which stabilizes the \gls{AVIS} but yields only moderate vibration isolation.
See \appref{app:avis-setup} for detailed information regarding both the experimental setup and the experimental controller.
The $r_1$ input consists of five periods of a random phase multisine of $65\,536$ samples with excited bins such that $\omega_k \approx 1.001 \omega_{k-1}$  and $\Ts=1\unit{ms}$.
See \chapref{sec:excitation} and \citep{Geerardyn2013TIM} for more information regarding the design of such a signal.

@@

The non-uniqueness of the \gls{RCF} can be exploited to satisfy additional conditions.
In view of the robust control criterion
\begin{equation}
  \Crit(\Plant,\Controller) 
    \isdef 
      \infnorm{W \ClosedLoop{\Plant,\Controller} V}
  \label{eq:lrmhinf:controlCrit}
  \text{,}
\end{equation}
the \glspl{RCF} are constructed such that
$
  \worstCase\Crit \left( \ModelSet[], \experimental\Controller \right)
  \leq
  \Crit \left( \estimated\Plant, \experimental\Controller \right)
  + \gamma
$
where $\worstCase\Crit(\ModelSet[],C) \isdef \sup_{P\in\ModelSet[]} \Crit(P,C)$~\citep{Oomen2012SIRP}.
% Obviously, $\Crit( \true\Plant, \experimental\Controller) \leq \worstCase\Crit ( \ModelSet[], \experimental\Controller )$ is guaranteed when $\true\Plant \in \ModelSet[]$.
I.e. even for a weighted control criterion \eqref{eq:lrmhinf:controlCrit}, there is no need to incorporate weights $W'$ and $V'$ into the estimation of the uncertainty bound as $\infnorm{W' \Delta V'}$.
In this chapter, an eighth-order $\estimated\Plant$~(\figref{fig:lrmhinf:avis-frf}) is estimated.
Some dynamics are left unmodeled and are hence part of $\Delta$~(\figref{fig:lrmhinf:avisMeas}).

>>>>

\subsection{Measurement \& Control Framework}
\label{sec:lrmhinf:control}
The experiments on the \gls{AVIS} are carried out in closed-loop (\figref{fig:lrmhinf:tpc}) with $r_2 = 0$.
The controller $\Controller=\experimental\Controller$ is a diagonal \gls{PI} regulator which stabilizes the \gls{AVIS} but yields only moderate vibration isolation.
See \appref{app:avis-setup} for detailed information regarding both the experimental setup and the experimental controller.
The $r_1$ input consists of five periods of a random phase multisine of $65\,536$ samples with excited bins such that $\omega_k \approx 1.001 \omega_{k-1}$  and $\Ts=1\unit{ms}$.
See \chapref{sec:excitation} and \citep{Geerardyn2013TIM} for more information regarding the design of such a signal.

@@

The non-uniqueness of the \gls{RCF} can be exploited to satisfy additional conditions.
In view of the robust control criterion
\begin{equation}
  \Crit(\Plant,\Controller) 
    \isdef 
      \infnorm{W \ClosedLoop{\Plant,\Controller} V}
  \label{eq:lrmhinf:controlCrit}
  \text{,}
\end{equation}
the \glspl{RCF} are constructed such that
\begin{equation}
  \worstCase\Crit \left( \ModelSet[], \experimental\Controller \right)
  \leq
  \Crit \left( \estimated\Plant, \experimental\Controller \right)
  + \gamma
\end{equation}
where $\worstCase\Crit(\ModelSet[],C) \isdef \sup_{P\in\ModelSet[]} \Crit(P,C)$~\citep{Oomen2012SIRP}.
$\ClosedLoop{\Plant,\Controller}$ denotes the closed loop transfer function from the loop inputs $\mat{r_2 & r_1}^{\TT}$ to the output and input of the plant $\mat{y & u}^{\TT}$ as schematically in \figref{fig:lrmhinf:tpc}.
This can be expressed symbolically, as in \citet{Oomen2012SIRP}, by
\begin{equation}
\ClosedLoop{\Plant, \Controller} \isdef
\begin{bmatrix}
  \Plant\\
  \I
\end{bmatrix}
\left(\I + \Controller \Plant \right)^{-1}
\begin{bmatrix}
\Controller & \I
\end{bmatrix}
\label{eq:lrmhinf:closedLoop}
\text{.}
\end{equation}
% Obviously, $\Crit( \true\Plant, \experimental\Controller) \leq \worstCase\Crit ( \ModelSet[], \experimental\Controller )$ is guaranteed when $\true\Plant \in \ModelSet[]$.
I.e. even for a weighted control criterion \eqref{eq:lrmhinf:controlCrit}, there is no need to incorporate weights $W'$ and $V'$ into the estimation of the uncertainty bound as $\infnorm{W' \Delta V'}$.
In this chapter, an eighth-order $\estimated\Plant$~(\figref{fig:lrmhinf:avis-frf}) is estimated.
Some dynamics are left unmodeled and are hence part of $\Delta$~(\figref{fig:lrmhinf:avisMeas}).
